---
title: "Morts Collisions"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
---

# Importations / nettoyage

```{r}
library(ggfortify)
library(lmtest)
library(dplyr)
library(ggplot2)
```


```{r}
wd <- set_wd()
```


```{r}
Total_et_Diro <- readr::read_csv(paste0(wd$data, 
                                        "derived/Total_et_Diro.csv"),
                                 locale = readr::locale(encoding = "UTF-8"))
Total_et_Diro <- Total_et_Diro %>%
  dplyr::select(-`...1`)
```

# Mortalit?s routi?res - Toutes donn?es
```{r}
Donnees <- Total_et_Diro %>%
  dplyr::filter(etat_biologique == "Trouv? mort : impact routier")
```

## Lapin

### Lapin - Sanglier
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 61714,
                   espece_benchmark = 60981)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### Lapin - Renard

```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 61714,
                   espece_benchmark = 60588)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```
### Lapin - Chevreuil
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 61714,
                   espece_benchmark = 61057)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### Lapin - Blaireau
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 61714,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

## H?risson

### H?risson - Sanglier
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60015,
                   espece_benchmark = 60981)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### H?risson - Renard
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60015,
                   espece_benchmark = 60588)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### H?risson - Chevreuil
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60015,
                   espece_benchmark = 61057)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### H?risson - Blaireau
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60015,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

## Putois

### Putois - Sanglier
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60731,
                   espece_benchmark = 60981)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### Putois - Renard

```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60731,
                   espece_benchmark = 60588)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```
### Putois - Chevreuil
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60731,
                   espece_benchmark = 61057)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### Putois - Blaireau
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60731,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```


## Hermine

### Hermine - Sanglier
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60686,
                   espece_benchmark = 60981)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### Hermine - Renard
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60686,
                   espece_benchmark = 60588)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### Hermine - Chevreuil
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60686,
                   espece_benchmark = 61057)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### Hermine - Blaireau
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60686,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

## Belette


### Belette - Sanglier
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60716,
                   espece_benchmark = 60981)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### Belette - Renard
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60716,
                   espece_benchmark = 60588)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### Belette - Chevreuil
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60716,
                   espece_benchmark = 61057)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### Belette - Blaireau
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60716,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```


## Fouine

### Fouine - Sanglier
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60674,
                   espece_benchmark = 60981)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### Fouine - Renard
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60674,
                   espece_benchmark = 60588)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### Fouine - Chevreuil
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60674,
                   espece_benchmark = 61057)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### Fouine - Blaireau
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60674,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

## Temoins

### Sanglier - Renard
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60981,
                   espece_benchmark = 60588)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### Sanglier - Chevreuil
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60981,
                   espece_benchmark = 61057)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### Sanglier - Blaireau
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60981,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```


### Renard - Chevreuil
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60588,
                   espece_benchmark = 61057)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

### Renard - Blaireau
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60588,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```


### Chevreuil - Blaireau
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 61057,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

# Mortalit? routi?res - DIRO uniquement

Il me manque la colonne bdd_originale... O? est elle pass??
