---
title: "Toutes données (Vu FN, GN, et Diro)"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
---

# Importations / nettoyage


```{r}
library(ggfortify)
library(lmtest)
library(dplyr)
library(ggplot2)
```


```{r}
wd <- set_wd()
```


```{r}
Total_et_Diro <- readr::read_csv(paste0(wd$data, 
                                        "derived/Total_et_Diro.csv"),
                                 locale = readr::locale(encoding = "UTF-8"))
Donnees <- Total_et_Diro %>%
  dplyr::select(-`...1`)%>%
  dplyr::filter(date < as.Date("2025-01-01"))
```

## Lapin

### Lapin - Sanglier
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 61714,
                   espece_benchmark = 60981)
```


```{r}
liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Y_10km + Famille_paysage_m + prop_tmoins1 +prop_tmoins2 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


### Lapin - Renard

```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 61714,
                   espece_benchmark = 60585)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```


```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + Famille_paysage_m + Dist_Ecotone + prop_tmoins1 +prop_tmoins2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```

### Lapin - Chevreuil

```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 61714,
                   espece_benchmark = 61057)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Famille_paysage_m + Dist_Ecotone + Dist_Littoral + Dist_Eau + prop_tmoins1 +prop_tmoins2 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```

### Lapin - Blaireau

```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 61714,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```


```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + Famille_paysage_m + Dnst_Cultures + Dist_Ecotone + prop_tmoins1 +prop_tmoins2 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```

## Herisson

### Herisson - Sanglier
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60015,
                   espece_benchmark = 60981)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Famille_paysage_m + Dist_Littoral + prop_tmoins1 +prop_tmoins2 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


### Herisson - Renard

```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60015,
                   espece_benchmark = 60585)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Famille_paysage_m + prop_tmoins1 + prop_tmoins2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


### Herisson - Chevreuil
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60015,
                   espece_benchmark = 61057)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Famille_paysage_m + prop_tmoins1 +prop_tmoins2 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


### Herisson - Blaireau
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60015,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```


```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Y_10km + Famille_paysage_m + Dnst_Cultures + prop_tmoins1 +prop_tmoins2 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


## Putois

### Putois - Sanglier
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60731,
                   espece_benchmark = 60981)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Famille_paysage_m + prop_tmoins1 +prop_tmoins2 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```

### Putois - Renard

```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60731,
                   espece_benchmark = 60585)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + prop_tmoins1)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


### Putois - Chevreuil
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60731,
                   espece_benchmark = 61057)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```


```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Y_10km + Dist_Ecotone + prop_tmoins1 + prop_tmoins2 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


### Putois - Blaireau
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60731,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```


```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + Famille_paysage_m + Dist_Ecotone + prop_tmoins1 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


## Hermine

### Hermine - Sanglier
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60686,
                   espece_benchmark = 60981)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```


```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Famille_paysage_m + Ind_Diversite + prop_tmoins1 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


### Hermine - Renard
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60686,
                   espece_benchmark = 60585)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + Dist_Ecotone + prop_tmoins1)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


### Hermine - Chevreuil
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60686,
                   espece_benchmark = 61057)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Famille_paysage_m + prop_tmoins1 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


### Hermine - Blaireau
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60686,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + Y_10km + Dist_Ecotone + prop_tmoins1 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


## Belette


### Belette - Sanglier
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60716,
                   espece_benchmark = 60981)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Famille_paysage_m + Dist_Eau + prop_tmoins1 +prop_tmoins2 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


### Belette - Renard
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60716,
                   espece_benchmark = 60585)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + Famille_paysage_m + Dist_Ecotone + Dist_Eau + prop_tmoins1 + prop_tmoins2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```

### Belette - Chevreuil
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60716,
                   espece_benchmark = 61057)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Famille_paysage_m + Dist_Ecotone + Dist_Eau + prop_tmoins1 +prop_tmoins2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


### Belette - Blaireau
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60716,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + Famille_paysage_m + Dnst_Cultures + Dist_Ecotone + Dist_Eau + prop_tmoins1 +prop_tmoins2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```

## Fouine

### Fouine - Sanglier
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60674,
                   espece_benchmark = 60981)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + prop_tmoins1 + prop_tmoins2 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


### Fouine - Renard
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60674,
                   espece_benchmark = 60585)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Famille_paysage_m)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```

### Fouine - Chevreuil
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60674,
                   espece_benchmark = 61057)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + Famille_paysage_m + Dist_Littoral + prop_tmoins1 +prop_tmoins2 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


### Fouine - Blaireau
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60674,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Ind_Diversite + prop_tmoins1 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```

## Temoins

### Sanglier - Renard
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60981,
                   espece_benchmark = 60585)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Famille_paysage_m + prop_tmoins1 +prop_tmoins2 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```

### Sanglier - Chevreuil
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60981,
                   espece_benchmark = 61057)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + Y_10km + Famille_paysage_m + Dist_Littoral + prop_tmoins1 + prop_tmoins2 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```

### Sanglier - Blaireau
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60981,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Famille_paysage_m + Dnst_Cultures + Dist_Ecotone + Dist_Littoral + prop_tmoins1 +prop_tmoins2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


### Renard - Chevreuil
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60585,
                   espece_benchmark = 61057)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Famille_paysage_m + Dnst_Cultures + Dist_Eau + prop_tmoins1 + prop_tmoins2 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


### Renard - Blaireau
```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 60585,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + Famille_paysage_m + Dnst_Cultures + Dist_Ecotone + prop_tmoins1 + prop_tmoins2 + year2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```


### Chevreuil - Blaireau

```{r}
bdd_reg <- tab_glm(Donnees, 
                   espece_interet = 61057,
                   espece_benchmark = 60636)

liste <- choisi_forme_year(bdd = bdd_reg)
regfit <- liste[1]$regfit
bdd <- liste[2]$bdd
```

```{r}
reg.summary <- summary(regfit); plot_regsubsets(reg.summary)
```

```{r}
par(mfrow=c(1 ,1)) ; plot(regfit, scale ="bic")
```

```{r}
reg <- glm(data = bdd,
           formula = proportion_interet ~ year + X_10km + Y_10km + Famille_paysage_m + Dnst_Cultures + prop_tmoins1 +prop_tmoins2)
```

```{r}
summary(reg); autoplot(reg)
bgtest(reg); bptest(reg) 
```
